---
title: "samovar-basic"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{samovar-basic}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(samovaR)
library(tidyverse)
```

# Download data

```{r}
teatree <- GMrepo_type2data(number_to_process = 5000)
viz_composition(teatree, interactive = T)
```

# Preprocessing

## Filter data

```{r}
tealeaves <- teatree %>%
  teatree_trim(treshhold_species = 3, 
               treshhold_samples = 3, 
               treshhold_amount = 10^(-4))

```

## Normalizing

If you build teatree by your own, do rescaling stage when building via `teatree$rescale()` or assigning `teatree$min_value` and `teatree$max_value` is required

Good approximation to normal distribution is required for `glm` generating methods

```{r}
teabag <- tealeaves %>%
  tealeaves_pack(normalization_function = function(x) log10(x+1))
```

## Clustering

Do hierarchical (deprecated) or aggregating clustering of species

Remember: if you want to re-filter, it is better to re-do welding stage to avoid crashes in future!

```{r}
concotion <- teabag %>%
  teabag_brew(min_cluster_size = 40, max_cluster_size = 150)
```

## Build samovar

```{r}
samovar <- concotion %>%
  concotion_pour()
samovar -> samovar_base
```

## Generate data

```{r}
new_data <- samovar %>%
  samovar_boil(N = 100, avoid_zero_generations = F)
```


```{r}
viz_composition(teatree, interactive = T)
```

